G85R vs WT (M + F)

### 2023-11-07 TKT_RNAseq/R Code/G85RvsWT_Analysis.Rmd
cami stuff

@@

specific.cat = specific.cat[2]
parent.category = 'neurogenesis'
specific.kegg = "DNA replication"
specific.go =  '32553'

@@

@@

  comparison.table = comparison.table[order(comparison.table$FDR),]
}
d
GRxWT.C = compare.conditions("E", "C")
GRxWT.Df = compare.conditions("D", "B")
GRxWT.OE = compare.conditions("F", "A")

@@

main.title = "Metabolites in G85R Males vs. WT Males"

@@

PathwayID = "04150"

ShowKEGG(PathwayID)

```{r echo = F, fig.align='center'}

knitr::include_graphics(paste0(OutputDir, "dme",PathwayID, ".", kegg.names[paste0("dme", PathwayID),1], ".png"))

>>>>

Synaptic = read.csv("/Users/johncsantiago/Documents/SynapticGenesandTFs.csv")

@@

specific.cat = specific.cat[1]
parent.category = 'neurogenesis'
specific.kegg = "DNA replication"
specific.go =  '32553'
Synaptic.genes = F

@@

volcano.data$Color = 'grey'
volcano.data$Color[volcano.data$Symbol %in% Synaptic$Symbol] = 'deeppink'

@@

  comparison.table = comparison.table[order(comparison.table$FDR),]
}

GRxWT.C = compare.conditions("E", "C")
GRxWT.Df = compare.conditions("D", "B")
GRxWT.OE = compare.conditions("F", "A")

@@

main.title = "FC for metabolites in G85R vs. WT"

@@
